The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-02-22 src/paper/theory.tex
Fix Typo

One can also obtain the total welfare of side $i$, as it is simply the number of entrants plus the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
\begin{align}
    \label{eq:W_star}
    W_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - \int_0^{n_i} \kappa_i(s) \ds.
\end{align}

>>>>

One can also obtain the total welfare of side $i$, as it is simply the number of entrants times the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
\begin{align}
    \label{eq:W_star}
    W_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - \int_0^{n_i} \kappa_i(s) \ds.
\end{align}
